---
title: "Applied Exercise 11 - Caravan"
author: "Group 15"
date: "2/28/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Applied Exercise 11

(a) Create a training set consisting of the first 1,000 observations,
and a test set consisting of the remaining observations.

```{r }
library(ISLR)
data(Caravan)
Caravan$Purchase <- ifelse(Caravan$Purchase == 'Yes',1,0)
Caravan$Purchase <- as.factor(Caravan$Purchase)
library(randomForest)
#Train <- Caravan[1:1000,]
#Test <- Caravan[-(1:1000),]
Train = sample(1:1000, 1000)
caravan.test = Caravan[-Train, "Purchase"]
```

(b) Fit a boosting model to the training set with Purchase as the
response and the other variables as predictors. Use 1,000 trees,
and a shrinkage value of 0.01. Which predictors appear to be
the most important?

```{r, warning=FALSE}
library(gbm)
set.seed (1)
boost.caravan <- gbm(Purchase~., data=Caravan[Train,], distribution="bernoulli", n.trees=1000, interaction.depth=4, shrinkage=0.01)
summary(boost.caravan)
```

(c) Use the boosting model to predict the response on the test data.
Predict that a person will make a purchase if the estimated probability
of purchase is greater than 20 %. Form a confusion matrix.
What fraction of the people predicted to make a purchase
do in fact make one?

```{r}
prob.boost <- predict(boost.caravan, newdata=Caravan[-Train,], n.trees=1000, type = 'response')
pred.boost <- ifelse(prob.boost > .2,1,0)
table(caravan.test,pred.boost)

```
~15.7% of persons predicted to make a purchase actually did

How does this compare with the results obtained from applying KNN or logistic regression to this data
set?

```{r,warning=FALSE}
library(caret)

Caravan$Purchase <- as.factor(Caravan$Purchase)
caravan.test <- as.factor(caravan.test)

knn_model <- train(Purchase~., data = Caravan[Train,], preProcess = c('center','scale'))
logistic_model <- glm(Purchase~., data = Caravan[Train,], family = binomial)


knn_prob <- predict(knn_model,newdata = Caravan[-Train,], type = 'prob')
knn_pred <- ifelse(knn_prob[2] > .2,1,0)
table(caravan.test,knn_pred)
logistic_prob <- predict(logistic_model,Caravan[-Train,],type = 'response')
logistic_pred <- ifelse(logistic_prob > .2,1,0)
table(caravan.test,logistic_pred)

```
21.4% of persons predicted by the KNN model made a purchase
16.6% of persons predicted by the logistic regression made a purchase 
